### 2017-02-02 conclusion.tex
Formatting corrections made

\begin{figure}
  \includegraphics[width=\textwidth]{conclusion.pdf}
  \caption[Irregularity production factors]{Summary of the main conclusions in this thesis.  The radar of interest (MCM) is highlighted.  Polar patches (orange) drift antisunwards across the polar cap following the background plasma convection (red contours).  Nighttime irregularity observation is enhanced for a positive IMF \(B_y\) component.  Production is maximized near the terminator.  Small-scale irregularity production surrounding a large-scale structure is found to exhibit both asymmetry and anisotropy.  Radars are most likely to observe this asymmetry if the patch is elongated along the radar boresight.}
  \label{fig:conclusion}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\textwidth]{conclusion.pdf}
  \caption[Irregularity production factors]{Summary of the main conclusions in this thesis.  The radar of interest (MCM) is highlighted in pink.  Polar patches (orange) drift antisunwards across the polar cap following the background plasma convection (red contours).  Nighttime irregularity observation is enhanced for a positive IMF \(B_y\) component.  Production is maximized near the terminator.  Small-scale irregularity production surrounding a large-scale structure is found to exhibit both asymmetry and anisotropy.  Radars are most likely to observe this asymmetry if the patch is elongated along the radar boresight.  Backscatter is most likely to be observed in a particular window of slant ranges within the radar FoV.}
  \label{fig:conclusion}
\end{figure}

### 2017-02-02 introduction.tex
Paper3 added to thesis
Formatting corrections made

Plasmas are fluid masses of charged particles, often formed when neutral atoms and molecules in a gas are ionized by external energy.  Instances of plasma include everything from fluorescent lightbulbs and flames to more exotic examples such as nuclear fusion reactor experiments, most stars, nebulas, and the interstellar medium.  In fact, about 99\% of visible matter in the known universe exists in the plasma state.  Of particular interest to this thesis is the plasma in the Earth's ionosphere.

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth,angle=180]{SuperDARNmap.pdf}
	\caption[SuperDARN map]{Fields-of-view of all operational SuperDARN radars in both the northern (left) and southern (right) hemispheres.  Polar-latitude radars are shown with the red outlines.  The radars at Rankin Inlet (northern hemisphere) and McMurdo Station (southern hemisphere) are shaded in red because these two instruments are particularly important to this body of work.  Lines of constant magnetic latitude are shown in yellow at \(\Lambda = 40\deg, 60\deg, 80\deg\) in the northern hemisphere and at \(\Lambda = -40\deg,-60\deg,-80\deg\) in the southern hemisphere.}
	\label{fig:superdarnmap}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{ISRmap.pdf}
	\caption[ISR map]{FoVs of all ISRs in the northern polar region.  The individual radars shown are identified by their commonly used acronyms: Poker Flat (PFISR), Resolute Bay North (RISR-N), Resolute Bay Canada (RISR-C), Sondrestrom (SFJ).  RISR-N, which is primarily used throughout this thesis, is shown in orange.  The FoV of the SuperDARN RKN radar is shown by the red outline.  Lines of constant MLAT are shown at \(\Lambda=80\deg,60\deg\) in yellow.}
	\label{fig:isrmap}
\end{figure}

>>>>

Plasmas are fluid masses of charged particles, often formed when neutral atoms and mol\-e\-cules in a gas are ionized by external energy.  Instances of plasma include everything from fluorescent lightbulbs and flames to more exotic examples such as nuclear fusion reactor experiments, most stars, nebulas, and the interstellar medium.  In fact, about 99\% of visible matter in the known universe exists in the plasma state.  Of particular interest to this thesis is the plasma in the Earth's ionosphere.

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth,angle=180]{SuperDARNmap.pdf}
	\caption[SuperDARN map]{Fields-of-view of all operational SuperDARN radars in both the northern (a) and southern (b) hemispheres.  Polar-latitude radars are shown shaded in blue.  The radars at Rankin Inlet (northern hemisphere) and McMurdo Station (southern hemisphere) are outlined in pink because these two instruments are particularly important to this body of work.  Lines of constant magnetic latitude are shown in yellow at \(\Lambda = 40\deg, 60\deg, 80\deg\) in the northern hemisphere and at \(\Lambda = -40\deg,-60\deg,-80\deg\) in the southern hemisphere.}
	\label{fig:superdarnmap}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{ISRmap.pdf}
	\caption[ISR map]{FoVs of all ISRs in the northern polar region.  The individual radars shown are identified by their commonly used acronyms: Poker Flat (PFISR), Resolute Bay North (RISR-N), Resolute Bay Canada (RISR-C), Sondrestrom (SFJ), European Incoherent Scatter Scientific Association (EISCAT), and EISCAT Svalbard (ESR).  RISR-N, which is primarily used throughout this thesis, is shown in orange.  The FoV of the SuperDARN RKN radar is shown by the pink outline.  Lines of constant MLAT are shown at \(\Lambda=80\deg,60\deg\) in yellow.}
	\label{fig:isrmap}
\end{figure}
